---
title: 'Stat 480 - Homework #10'
author: "Your Name"
date: "4/5/2018"
output: html_document
---
---
title: 'Stat 480 - Homework #10'
author: "Your Name"
date: "4/5/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Statistical movie consultant

1. Download the RMarkdown file with these homework instructions to use as a template for your work.
Make sure to replace "Your Name" in the YAML with your name.
2. For this homework you should start by using the data sets `box` and `budget` from the `classdata` package, which consists of weekly box office gross for movies of the last five year and information on the ~5000 movies with the highest production budgets.

```{r, message=FALSE, warning=FALSE}
# devtools::install_github("heike/classdata")
library(classdata)

head(box)
```

3. Imagine that you are working for a statistical consulting company that wants to land a contract with a medium sized movie distributor (you can pick a distributor, if you want). Your job is to make a pitch to the company about what you could do for them in terms of data exploration. For that, your boss asks you to describe in one page of write-up (including 1-2 visuals) 'something interesting' about the movie industry.

Make sure that your writeup is comprehensive: you need to (a) motivate and describe your line of inquiry, (b) describe the relevant data source(s), and (c) describe your findings.

This homework is going to be graded on three metrics: curiosity, skepticism, and organization:<br>
*curiosity*: Ideally you demonstrate an intense exploration with (some) evidence of trials and failures. 
Present best ideas, rather than all ideas. Additional research from other sources 
used to help understand/explain findings.<br>
*scepticism*: Demonstrate that you are critical of findings, use multiple approaches and techniques to verify unintuitive results.<br>
*organization*: Findings are well organised with a clear structure. Clear evidence of systematic analysis. Charts and tables are optimized for the use.

In each of the three metrics you can get a maximum of 3 points. The last point for the homework is determined by whether your findings are completely (computationally) reproducible.


Due date: the homework is due before class on Thursday. 

For the submission: submit your solution in an R Markdown file and (just for insurance) submit the corresponding html file with it. 
